Unsupervised Learning for Identifying Events in Active Target Experiments

### 2020-08-06 doc/Manuscript/article.tex
Updates from Overleaf

The AT-TPC data we studied for this work was recorded as charge time-series for each of the  the $\sim10^4$ detector pads.
In this representation, an event is a record of $512$ time-buckets for each of the $10^4$ detector pads. In our analysis, we represent each event as a down-sampled two-dimensional  projection.
We chose to represent the data in two dimensions to facilitate the use of advanced image-recognition machine learning models, and this data representation was shown to successfully classify the events of this experiment in a supervised setting \cite{Kuchera2019}.
First, the time-series data was represented as a three-dimensional  point cloud, where each point contains the maximum charge in the time-series trace. We log-transform and map the data to the interval $[0, 1]$. The data is projected into a two-dimensional  space by summing over the time-axis. Thereafter the data is down-sampled into a $128\times128$ pixel image.
%Additionally, we log-transform and normalize the data to the interval $[0, 1]$ for each point. The final representation for each event is a $128 \times 128$ matrix with each element ranging from $0$ to $1$.

@@

%{\color{orange}[RS Another abrupt end to a paragraph. Could probably use some rounding out.]}

>>>>

The AT-TPC data we studied for this work was recorded as charge time-series for each of the  the $\sim10^4$ detector pads.
In this representation, an event is a record of $512$ time-buckets for each of the $10^4$ detector pads. In our analysis, we represent each event as a down-sampled two-dimensional  projection.
We chose to represent the data in two dimensions to facilitate the use of advanced image-recognition machine learning models, and this data representation was shown to successfully classify the events of this experiment in a supervised setting \cite{Kuchera2019}.
First, the time-series data was represented as a three-dimensional  point cloud, where each point contains the maximum charge in the time-series trace. We log-transform the data and perform a min-max scaling in order to  map the data to the interval $[0, 1]$. The data is projected onto a two-dimensional  space by summing over the time-axis. Thereafter the data is down-sampled into a $128\times128$ pixel image.
%Additionally, we log-transform and normalize the data to the interval $[0, 1]$ for each point. The final representation for each event is a $128 \times 128$ matrix with each element ranging from $0$ to $1$.

@@

%{\color{orange}[RS Another abrupt end to a paragraph. Could probably use some rounding out.]} 
\subsection*{Acknowledgements}
MHJ’s work is supported by U.S. National Science Foundation Grants No. PHY-1404159 and PHY-2013047.
